\documentclass[11pt]{article}
\usepackage{fullpage}

\title{\bf An open letter concerning \\
\vspace{5mm}{Subspaces that Minimize the Condition Number of
a Matrix}}
\author{Siddharth Joshi \and Stephen Boyd}
\date{} 

\begin{document}
\maketitle
\thispagestyle{empty}

This article poses and answers the following question: 
How do you choose a subspace
of given dimension that minimizes the
condition number of a given matrix on that subspace?
Part of the answer is a bit surprising
(at least to us):  When  the subspace dimension is
no more than half the size of the matrix, a subspace can be
found on which the matrix has condition number one.

We think our paper makes it clear that we consider our result
simple, but interesting and not obvious.  We certainly make no claims as to
its depth, or its potential applications.
It is not in the literature, and does not follow
in any direct or simple way from existing results.
In other words, it is, as far as we know, new.

The manuscript was rejected by two journals.
The first rejection was based on the reviewers and editor
noting that someone had written a paper that seemed to cover
similar material.  But a cursory reading of that paper, and ours,
show that while the other paper shared a few key words with ours,
the results were in no way related.
On the positive side, one reviewer suggested a simplification of
our proof, which we gladly used in our revision, which was also
rejected.

We then submitted the article to another journal. 
In this case, the editor apparently did not even understand the
result, which is stated very clearly, in completely standard,
and elementary, mathematical language.
Moreover, he insisted that we describe an application, so we added
a simple application involving an ellipsoid intersected with
a subspace.  It was rejected.

\end{document}
