\documentclass[12pt]{article}
\usepackage{fullpage}

%Added by Jaska
\topmargin 0.0in
\headheight 0.0in
\pagestyle{empty}
%%%%%%

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title, author, and institution information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\bf An open letter concerning \\
\vspace{5mm}{\em Alexander duality for monomial ideals and their resolutions}}
\author{}%\large\em Ezra Miller}
% 
\date{}%25 February 2008} % No date

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\thispagestyle{empty}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
Dear Reader,

\medskip

\noindent
This article was submitted to Journal of Pure and Applied
Algebra on December 15, 1998, and it was rejected with a very  
short report about eight months later, the cited reason being
that it was too long for its content.  By the time I received
that overdue rejection, I was nearly done writing a sequel,
\begin{list}{}
\item
  Ezra Miller, \emph{The Alexander duality functors and local
  duality with monomial support}, Journal of Algebra
  \textbf{231} (2000), 180--234.
\end{list}

\bigskip
\noindent
which contained more general results.  The sequel has been
well-cited, but the current article was already on the arXiv
(math.AC/9812095), and according to Google Scholar it has also
been well-cited.  In fact, this article has been cited more
than most of my others---as much or more, for example, than my
articles in Journal of the American Mathematical Society and Duke
Mathematical Journal.  It seemed a shame that what is
apparently a useful article should languish in eternal
semipublication, so I submitted it to Rejecta Mathematica.

\medskip
\noindent
Why is this article useful?  It is more concrete than its
sequel: more examples, more illustrations, and fewer functors.
The article contains no known errors and no known uncited
rederivations of earlier work; in fact, subsequent work (by
other authors as well as in its sequel) has confirmed the
results herein by independent methods many times over.  The
article is unchanged from the version submitted to Journal of
Pure and Applied Algebra.

\bigskip
\bigskip
\noindent\hspace{4in}Ezra Miller

\smallskip
\noindent\hspace{4in}25 February 2008

\end{document}
